%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Vinay Raghavan K S
% Uses PDFLaTeX and moderncv 
% [http://www.ctan.org/tex-archive/macros/latex/contrib/moderncv/]
% To generate the resume in .pdf format, run pdflatex <filename>
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper,sans]{moderncv}
%\moderncvtheme[purple]{classic}
\moderncvtheme[blue]{classic}
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
%\moderncvstyle{casual}                             

% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 
% 'grey' and 'black'
%\moderncvcolor{blue}

% char encoding
\usepackage[utf8]{inputenc}

% page margin adjustments
\usepackage[scale=0.88888888]{geometry}

%\usepackage{hyperref} % Not required now, as used url package

\usepackage{url}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
% required when changes are made to page layout lengths
\AtBeginDocument{\recomputelengths} 

% personal data
\firstname{Vinay Raghavan}
\familyname{K S}
\title{Résumé}  
\address{}{Bangalore, India}
\mobile{+91-9986031265}
\email{root@rghv.in}
\secemail{raghavan.vinay@gmail.com} 
%Modified the .cls and classic sty to have a newcommand \secemail
\homepage{rghv.in}
%\extrainfo{\url{linkd.in/11Qhxir}}
% '64pt' is the height the picture must be resized to and 'picture' is the 
% name of the picture file;
%\photo[54pt]{img.jpeg}    
\social[linkedin]{vinayraghavan}    
\social[github]{rghv}             
%\social[twitter]{\_raghava\_}      
%\extrainfo{additional information}     
%\photo[48pt][0.0pt]{img}                       % optional, remove / comment 
% the line if not wanted; '64pt' is the height the picture must be resized to, 
% 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) 
% and 'picture' is the name of the picture file
% \quote{"Always pass on what you have learned" - Master Yoda}                            

% --------------------------------------
% CONTENT
% --------------------------------------
\begin{document}
\maketitle

\definecolor{linky}{HTML}{0000AA}
\newcommand\colorhref[3][linky]{\href{#2}{\small\color{#1}#3}}

% --------------------------------------
% ze Skillies and stuffies  
% --------------------------------------
\section{Technical skills}
\cvcomputer
{\textbf{Operating Systems}}{Gnu/Linux (various flavours), HP-UX, Sun\
	Solaris, IBM AIX, MS Windows}
{\textbf{Programming Languages}}{C, C++, Python, UNIX Shell scripting,\
	Perl, Java, Javascript}
\cvcomputer
{\textbf{Development Tools}}{Vim, CVS, svn, Hg, bash, ksh, Eclipse,\
Cygwin, gdb/dbx/wdb, pdb, \textrm{\LaTeX}}
{\textbf{Databases}}{Oracle, MySQL}
\cvcomputer
{\textbf{Enterprise Software}}{
	\hypersetup{linkcolor=blue}
	\colorhref{finacle.com}{Finacle} suite of banking products, ThunderHead\
Document Automation System, BIH Data Integration Platform}
{\textbf{Software utilities}}{IBM WAS, Apache suite, Google App Engine,\
sed, awk, Rational Purify suite, HP FireBolt suite}
\cvcomputer
{\textbf{Experienced in}}{Systems Integration, Performance Engineering,\
	Interfaces Design and Implementation, Metaprogramming, Toolchain Design and\
	Development, Test Automation Framework Design and Implementation,\
	Build and Release Framework Development, Systems and Workflow Design,\
	Code coverage and profiling, OOAD-OOP, SOA frameworks, Test Driven\
	Development}
{\textbf{Domain}}{Retail Banking, Financial Systems, Reporting and\
Document Generation}
{}{}

% --------------------------------------
% EDUMACATION!!! 
% --------------------------------------
\section{Education}

%1
\cventry
{September 2001 -- July 2005}
{Bachelor of Engineering}
{Computer Sciences and Engineering}
{VTU Belgaum}
{First Class}
{} 

%2
\cventry
{June 2001}
{AISSCE, Class XII}
{CBSE}
{Distinction}
{}
{} 

%3
\cventry
{June 1999}
{AISSE, Class X}
{CBSE}
{Distinction}
{} 
{}

% --------------------------------------
% WORK EXPERIENCE
% --------------------------------------
\section{Work Experience \& Career Chronology}
%1
\cventry
{January 2013 -- Present}
{Independent Programmer}
{Programming and Independent Technology Consulting}
{Bangalore}
{}
{Providing technology consulting and freelancing in the meantime,\
	specializing in open-source technologies. Exploring various new\
	technologies in parallel.
%\newline{}
%\newline{}
%\small {\textbf{Tools/Technologies:}\
%C, Python, Linux, Shell scripting, Web programming} 
\newline{}
}
%2
\cventry
{October 2011 -- December 2012}
{Product Technology Lead - ANZ Singapore Implementation Team}
{Systems Integration Team, Finacle}
{\colorhref{infosys.com}{Infosys Ltd, Singapore}}
{} 
{Designed and implemented enhancements to systems interfaces from Finacle to\
various \colorhref{anz.com}{ANZ} systems (ThunderHead, BIH etc), providing\
complete automation of statement, advice and report generation with a\
non-native interface from Finacle to ANZ systems. \\
As an implementation consultant part of Finacle-ANZ implementation team,\
designed and implemented solutions for various software enhancements and\
customization to existing interfaces between ANZ and Finacle Core Banking\
systems.
\newline{}
\newline{}
\small {\textbf{Role:} Led and mentored a team of developers and\
	analysts as a Team Lead and Implementation Consultant, for design\
	and development of enhancements and customization for ANZ Foundation\
Programme and ANZ Philippines/HK.}
\newline{}
\small {\textbf{Tools/Technologies:}\
C, C++, Python, Java, UNIX, Shell scripting, Finacle scripting, XML,\
BIH/TH systems, Javascript, Oracle.} 
\newline{}
}
%3
\cventry
{April 2010 -- September 2011}
{Product Technology Lead - Finacle Core Engg., Mysore}
{Tech Lead - Localization Framework, Finacle Technical Delivery Group}
{\colorhref{infosys.com}{Infosys Ltd, Mysore}}
{}
{Designed and implemented enhancements and new features in internal tools,\
infrastructure and frameworks for the newly carved Localization layer for\
the Finacle product. End to end implementation of extension of tools for\
Localization layer provided ability to design/code/implement/package\
geographic locale specific solutions within the Finacle CBS. As part\
of the systems optimization project handled performance enhancements\
for the product.
\newline{}
\newline{}
\small {\textbf{Role:} Led and mentored a team of developers and analysts\
	as a Product Lead, for design and development of Localization layer of the\
	Finacle CBS.}
\newline{}
\small {\textbf{Tools/Technologies:}\
C, C++, Python, Java, UNIX, Shell scripting, Finacle scripting, XML,\
Purify suite, Oracle.} 
\newline{}
\small {\textbf{Accolades}: Awarded the quarterly GEM award for Team\
Excellence.}
\newline{}
}
%4
\cventry
{October 2009 -- March 2010}
{Technology Analyst - Finacle Core Engg., Mysore}
{Finacle 10 Beta Build and Release Ops, Finacle Technical Delivery Group}
{\colorhref{infosys.com}{Infosys Ltd, Mysore}}
{}
{Implemented features and enhancements to Finacle CBS build and patching\
systems, patch maintenance systems and related internal tools and\
infrastructure. Part of the most ambitious Finacle 10 Beta Program that\
offered a host of new features and improvement in productivity of\
Finacle CBS. 
\newline{}
\newline{}
\small {\textbf{Role:} Led a team of developers as a Lead Developer, for\
	design and development of enhancements to build, release and patching\
	systems of Finacle CBS.}
\newline{}
\small {\textbf{Tools/Technologies:}\
C, C++, Python, Java, UNIX, Shell scripting, Perl, Build and Release\
toolkit (internal), Test Automation framework (internal), Finacle scripting,\
Oracle.} 
\newline{}
\small {\textbf{Accolades}: Awarded the quarterly GEM award for Team\
Excellence.}
\newline{}
}
%5
\cventry
{October 2008 -- September 2009}
{Module Lead - Finacle Core Engg., Mysore}
{Finacle 10 Beta Program, Finacle Core Engg}
{\colorhref{infosys.com}{Infosys Ltd, Mysore}}
{}
{As Module Lead being part of Finacle 10.1 Beta program, implemented a\
host of new features and enhancements to the product. Design and\
implementation of Restricted Account Access Monitoring System and\
Foreign Cheques collection module, to name a few. Dabbled with\
OpenSolaris to roll out a custom distro for Finacle development.
\newline{}
\newline{}
\small {\textbf{Role:} Led and mentored a team of developers as a Lead\
	Developer, for design and development of new features and enhancements\
  for Finacle CBS.}
\newline{}
\small {\textbf{Tools/Technologies:}\
C, C++, Python, Java, UNIX, Shell scripting, Build and Release toolkit\
(internal), Finacle scripting, Javascript, Oracle.} 
\newline{}
\small {\textbf{Accolades}: Awarded the quarterly GEM award for Team\
Excellence}
\newline{}
}
%6
\cventry
{July 2005 -- September 2008}
{Software Engineer - Finacle Core Engg., Mysore}
{}
{\colorhref{infosys.com}{Infosys Ltd, Mysore}}
{}
{Started off as rookie software engineer in Finacle business unit.\
Implemented a host of new features and functionality in the\
Wealth Management Systems module of the Finacle CBS. Implemented\
enhancements to internal tools and frameworks.
\newline{} 
\newline{}
\small {\textbf{Role:} Developer; designing and implementing new features\
to WMS module of Finacle CBS.}
\newline{}
\small {\textbf{Tools/Technologies:}\
C, C++, Java, UNIX, Shell scripting, Finacle scripting, Oracle, Javascript.} 
\newline{}
}

% --------------------------------------
% AVAILABILITY 
% --------------------------------------
\section{Availability}
\cvlistitem
{\textit{\emph{Immediate}; no notice period.} 
}

% --------------------------------------
% PROJECTS
% --------------------------------------
%\pagebreak
\section{Projects of Interest}
\cvlistitem
{\textbf{ReqBlood - an app to tweet blood requests over SMS} 
  \\A recently developed app to allow people to tweet a blood request\
    through an SMS to 55444.\\
		{\small {\url{twitter.com/reqblood}}} \\
		{\small Uses: Python, Google App Engine, 55444 SMS platform} 
}
\cvlistitem
{\textbf{Dhvani TTS}  
  \\A TTS system for Indic languages. Contributed in testing \
		and minor fixes.\\
		{\small {\url{dhvani.sourceforge.net}}} \\
		{\small Uses: C, GNU/Linux, Python}
}
\cvlistitem
{\textbf{Chiguru Linux}  
  \\A volunteer effort as part of a group of technology enthusiasts that \
		rolled out a Linux distro targeted at Kannada users.\\
		{\small {\url{sourceforge.net/projects/kannada/files/Chiguru/}}} \\ 
		{\small Uses: GNU/Linux, Remastering utilities, shell scripting, Python } 
}

% --------------------------------------
% TALKS EVENTS ETC.
% --------------------------------------
\section{Talks given, Workshops/events participated in}
\cventry{April 2008}{GNU/Linux Habba}{SERC, IISc, Bangalore}{}{}
{Presented a talk on GNU/Linux for Kannada users. \\
Hands-on workshop on various utilities available for Kannada on Linux.}
\cventry{September 2008}{GNU/Linux Habba 2.0}{University of Mysore, Mysore}{}{}
{Presented a talk on FOSS utilities/alternatives for students.} 
\cventry{February 2009}{GNU/Linux Habba 3.0}{NMAMIT, NITTE}{}{}
{Presented a talk on FOSS utilities for engineering students. \\
Participated in development and launch of Chiguru Linux, a distro\
made for Kannada users.}

% --------------------------------------
% INTERESTS / HOBBIES
% --------------------------------------
\section{Interests and Hobbies}
\cvlistitem{A staunch believer and an enthusiast of FOSS/Open Source\
philosophy/software.\\}
\cvlistitem{An avid reader on technology, non-fiction books and websites.\\}
\cvlistitem{Hobbyist digital artist.}

%---------------------------------------
% Personal Details 
% --------------------------------------
\section{Other details}
\cvlistitem{Date of Birth   : 12 September 1983\\}
\cvlistitem{Nationality     : Indian\\}
\cvlistitem{Valid passport  : Available\\}

%---------------------------------------
% References? 
% --------------------------------------
\section{References}
\cvlistitem{Can be provided upon request.}

%---------------------------------------
% DECLARATION 
% --------------------------------------
\section{Declaration}
\cvlistitem{I hereby declare that the information furnished above is true\
to the best of my knowledge and belief.\\ \\}

\begin{minipage}{0.5\textwidth}
\begin{flushleft}
  \large
\bfseries Bangalore
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}

\begin{flushright}
  \large
\bfseries Vinay Raghavan \textsc{K S}
\end{flushright}
\end{minipage}

% --------------------------------------
% END
% --------------------------------------
\end{document}
